---
title: "linear model from Web"
author: "Kevin Brandon Salazar"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction
We predict a stimulated strength score based on arm and grip strength. We will find three models and compare them. The response variable is numerical and the explanatory variable is numerical, so we use the Num~Num helper file. 

So Among the three models (Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP) we'll figure out which is best. Then we will compare the three using Anova.



## Model 1 SIM~ARMS

## Results
### Graphical Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

This graph shows that as arm strength goes up the simulation score goes up also.

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation coefficient is 0.69 which shows that arm strength is related to sim score.

### Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
Both $b_0$ (The Intercept) and $b_1$ (The coefficient of arm strength) are significantly different from 0 because their P-values are very small


### Prediction Interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIM score. This shows that if we repeat this test multiple times with arm strength being 88 and grip strength 94 it will fall within that interval 95% of the time.

## Model 2 SIM~GRIP
## Results
### Graphical Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='green')
```

This graph shows that as grip strength goes up the simulation score goes up, Also the spread of the points around the regression line in the grip plot are more spread out than that of the arm strength plot.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
The correlation coefficient is 0.64 which shows that grip strength is related to sim score.


### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  
Both $b_0$ (The Intercept) and $b_1$ (The coefficient of arm strength) are significantly different from 0 because their P-values are very small

### Prediction Interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```
The prediction interval is from -3.1 to 2.0 for SIM score. This shows that if we repeat this test multiple times with arm strength being 88 and grip strength 94 it will fall within that interval 95% of the time. 


## Model 3 SIM~ARM+GRIP
## Results

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
The correlation coefficient is 0.73 which shows that grip strength is related to sim score.

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```  
Both $b_0$ (The Intercept) and $b_1$ (The coefficient of arm strength) are significantly different from 0 because their P-values are very small

### Prediction Interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.3, newdata, interval="predict")
```
The prediction interval is from -2.1 to 2.4 for SIM score. This shows that if we repeat this test multiple times with arm strength being 88 and grip strength 94 it will fall within that interval 95% of the time.

## Comparing nested models ANOVA Test

## Informally compare Model.1 with model.2
```{r}
anova(model.3, model.1)
```
The P value is 0.00000499 so I reject the null hypothesis so that means one of the models is better than another therefore I conclude that model 1 is better because rss for model one is smaller.

```{r}
anova(model.3, model.2)
```
The P value is so small I reject the null hypothesis so that means one of the models is better than another therefore I conclude that model 1 is better because rss for model one is smaller than both model three and two.

# Discussion / Conclusion
The original question was model sms and figure out which model works better at proving it by having a smaller rss compared to the other available models. Based on the tests that we've conducted we can conclude that the model with sim~arm+grip is the best since it has a smaller rss compared to the other models.
