---
title: "linear model from Web"
author: "Kevin Brandon Salazar"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction
We predict a stimulated strength score based on arm and grip strength. We will find three models and compare them. The response variable is numerical and the explanatory variable is numerical, so we use the Num~Num helper file. 

So Among the three models (Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP) we'll figure out which is best. Then we will compare the three using Anova.



## Model 1 SIM~ARMS

## Results
### Graphical Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

This graph shows that as arm strength goes up the simulation score goes up also.

### Numerical Results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation coefficient is 0.69 which shows that arm strength is related to sim score.

### Inferential Results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
Both $b_0$ (The Intercept) and $b_1$ (The coefficient of arm strength) are significantly different from 0 because their P-values are very small


### Prediction Interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIM score.

## Model 2 SIM~GRIP
## Results
### Graphical Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='green')
```

This graph shows that as grip strength goes up the simulation score goes up, Also the spread of the points around the regression line in the grip plot are more spread out than that of the arm strength plot.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
The correlation coefficient is 0.64 which shows that grip strength is related to sim score.


### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  
Both $b_0$ (The Intercept) and $b_1$ (The coefficient of arm strength) are significantly different from 0 because their P-values are very small

### Prediction Interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```
  


## Model 3 SIM~ARM+GRIP
## Results

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```  


### Prediction Interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.3, newdata, interval="predict")
```
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

